Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-06-03 structured.tex
2015.06.03 (Mema & Vassilis) Mema's latest pass. Also added paper for citation LCCLS2002.

This global view of the network state is used by organizing it into ``maps'' for
regions of the overlay, that are strategically placed
across the network and made available to any node. The notion of a
region is a well defined property for structured \p\ networks and can be part of
the Cartesian space in overlays like \emph{eCAN}~\cite{xu_ecan_2002} or a set of
nodes sharing a particular prefix in overlays such as
\emph{Pastry}~\cite{antony_pastry_2001}. Moreover, a node may appear in a maximum
of $log(N)$ such maps.

Direct access to this information, also coined \emph{soft states}, helps nodes
find the best way to route their messages, while a publish/subscribe mechanism
allows them to get notified on dynamic network changes.

@@

such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 

@@

During bootstrap, an incoming peer $J$ obtains from a bootstrap node a set of
candidate peers to establish links with. 
Subsequently, the node works iteratively to identify peers that minimize
a given metric (i.e., network delay).
The process stops when no additional peers complying with the above metric 
can be found. 
% 
% and iteratively
% probes for minimizing distances, based on a given metric (i.e., network delay)
% and concluding when no further refinement can be achieved. 
To tackle the local
minima problem that such a gradient descent method suffers from, Mithos probes
nodes within a $2$-hop radius from the current node that helps minimize
the distance before concluding the process.

$J$ is then assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close-by $2$-$d$ neighborhood as
this was discovered during the aforementioned phase. % iterative selection phase.
The benefit of adopting synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. 
Mithos proceeds then to designate $J$'s closest neighbors as 
previous steps do not reveal with certainty which these nodes are.
%%
Using Mithos \emph{quadrant-based} mechanism,
$J$  divides the $2$--$d$ space of neighbors in four regions and 
subsequently, establishes a link 
to the closest neighbor in each quadrant of the plane. 
% With peer $J$ dividing the plane into four regions,
% the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
% establishes a link to the closest neighbor in each quadrant of the plane. 
%%
It does so, by starting from a known node in the neighborhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node (i.e., number of links). 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4) with
each octet ranging from $1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

In order to optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia}~\cite{maymounkov_kademlia_2002} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by:
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with others, or 
  \item using a local database to look--up information.
\end{inparaenum}

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only a $6\%$ 
to go through the backbone.
The behavior of \cite{KLKP2008} with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\emph{CHOP6} \cite{MT2007} is a Chord-variant DHT that exploits
{\sl IPv6} address format as well as available \emph{RTT} information to 
enable proximity estimation among peers during message routing.
%%
Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table with each entry now holding $k$$>$$1$ candidate
nodes. 
The next hop for a message is selected to be the one closest to the
destination among those $k$ candidate peers. 
This proximity is determined either
by exploiting RTT measurements or, if there is no such information yet 
(i.e., a new peer appears), by
estimating distance on the overlay's ID space.

When joining the network, each node
receives a $64$-bit \emph{ID}. 
It comprises of a random part and the IPv6 prefix which 
is obtained by hashing the node's IP address and port
number; this combination is deployed in an effort  
to preserve the uniformity of node assignment. 
The prefix in question is based on IPv6's global routing prefix.
As IANA\footnote{\url{http://www.iana.org/}}  
assigns address blocks to regions (RIRs) which are further
distributed at national level (NIRs), the first $32$-bits of the address
can estimate the region or the country the node is connected in. 
Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing. 
%%
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the three qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
Inter-\emph{AS} links are the costliest to ISPs and hence, 
minimizing topology mismatches greatly affects pertinent operational expenditure.
%%
To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demonstrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portraying distance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
In this respect, administrators frequently
disable {\sl traceroute} support on their routers this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbors into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{PChord}
\emph{PChord} \cite{HLYW2005} is based on the \emph{Chord DHT} and adds
proximity into its routing mechanism. 
To achieve that, the standard finger table
is augmented with a \emph{proximity list} that contains
nodes in the network found close-by in terms of RTT.
%in this way, the next hop can be decided based on both progress
%towards the key and the physical proximity of the candidate nodes.
%%AD
%% I am not sure about the "best progress" term - what does it really mean???
%% VM changed the above slightly to address the above comment. Generally
%% in DHTs when a node receives a search query for a key that it does not have
%% the data for, it routes the request to that node in its routing table that
%% is closest to the key. That is what I mean with best progress to the keys
%% In topology aware systems and topology aware routing we have the requirement
%% that the next hop should be the closest one which in many cases can be
%% a competing requirement with the best progress to the key requirement I
%% just described. 
In this respect, the next hop during routing can be decided based on both the
direction towards the search key and minimizing the cost of that hop.

When a peer joins the network, its proximity list is empty.
This list is maintained in a heuristic fashion during the node's lifetime.
While a node attempts routing, the next hop is selected
as the closest node to the target key 
from \emph{both} its finger table and proximity list. 
An initial choice for the next hop made out of the finger list 
can be substituted by a shorter one from the proximity list if  
it is both closer to the key and in less physical distance.
This yields an equal or even more efficient routing than traditional Chord.
%% VM
%% Removed the text below that was a rephrasing of one of my own a little
%% bit more below. Hope it is way more clear now.
%%
% As there is always progress towards the target in the \emph{ID}-space,
% \emph{PChord} yields a reduced number of hopes that \emph{Chord}.
%%AD rephrased as above - the 2 last lines of the text below are 
%%		are difficult to decipher... 
% Due to the fact that, with each step, there is always 
% progress towards the target node in the ID space, 
% \emph{PChord} will result in a reduced hop number than
% Chord, since each hop in \emph{PChord} is larger or 
% at least equal in the key space.

@@

The \emph{ID} of an incoming node is computed based on 
both the identifier of the bootstrap node 
and the bootstrap's predecessor;
this is  done in a way that the \emph{ID} of the 
incoming peer is positioned \emph{between} the two identifiers mentioned above. 
After joining, a \emph{finger} table is created ala \emph{Chord}. 
Moreover, an \emph{adjacency table} maintains 
information about the $k$ closest--known peers. 
%%
The routing decision takes place in a way reminiscent to \emph{Chord}
and uses both adjacency and finger tables.
%%
\emph{AChord} behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% good routing efficiency but no adaptation to high churn environments.
medium &
% Relieves the system from joining overhead and topology aware ID construction
% but doubles the information needed to be stored and maintained by the
% introduction of adjacency table
medium &
% assumes the operation of ideal underlying any-cast mechanism (meaning that
% outside messages are always routed to the nearest node which in the current
% Internet, this is not always feasible. Moreover, is designed on the basis of
% IPv6 protocol which is not widely operational yet.
medium
\end{tabular}
}
\end{center}

@@

\emph{Chord6} does reduce the average 
length of hops traversed
% system path length 
to be logarithmically proportional to the number 
of available domains instead of the number of participating peers. 
Due however to the large number of Internet
domains and the possibility of occasionally having only 
a small number of peers within each domain,
\cite{DK2006} challenges the approach's scalability and efficiency.
%%
Overall, the approach fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Can reduce inter-domain average path length but even though nodes in the same
% domain would have close identifiers, nodes in two close domains may have very
% different ones reducing the overall efficiency of the approach in general when
% considering inter-domain average path length. No active adaptation mechanism
% for high churn environments.
low &
% The construction of the identifier space is done at node join and in an
% independent fashion involving the application of two hash functions meaning
% resulting in low overhead stress to the network and its nodes.
low &
% Is designed on the basis of IPv6 protocol which is not widely operational yet.
low
\end{tabular}
}
\end{center}

>>>>

This global view of the network state is used by organizing it into ``maps'' for
regions of the overlay, that are strategically placed
across the network and made available to any node. The notion of a
region is a well-defined property for structured \p\ networks and can be part of
the Cartesian space in overlays like \emph{eCAN}~\cite{xu_ecan_2002} or a set of
nodes sharing a particular prefix in overlays such as
\emph{Pastry}~\cite{antony_pastry_2001}. Moreover, a node may appear in a maximum
of $log(N)$ such maps.

Direct access to this information, also coined \emph{soft states}, helps nodes
find the best way to route their messages, while a publish/subscribe mechanism
allows them to get notified about dynamic network changes.

@@

such maps incurs additional traffic for probing and notifications
and so renders the approach unscalable \cite{RGJZ2004}. 

@@

During bootstrap, an incoming peer $J$ obtains from a bootstrap node a set of
candidate peers with which to establish links. 
Subsequently, the node works iteratively to identify peers that minimize
a given metric (i.e., network delay).
The process stops when no additional peers complying with the above metric 
can be found. 
% 
% and iteratively
% probes for minimizing distances, based on a given metric (i.e., network delay)
% and concluding when no further refinement can be achieved. 
To tackle the local
minima problem that such a gradient descent method suffers from, Mithos probes
nodes within a $2$-hop radius from the current node that helps minimize
the distance before concluding the process.

$J$ is then assigned a synthetic \emph{ID} that
represents the state of minimum distance from its nearby $2$-$d$ neighborhood 
discovered during the aforementioned phase. % iterative selection phase.
The benefit of adopting synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. 
Mithos then proceeds to designate $J$'s closest neighbors as 
previous steps do not reveal with certainty which nodes are its closest
neighbors.
%%
Using Mithos \emph{quadrant-based} mechanism,
$J$  divides the $2$--$d$ space of neighbors in four regions and 
subsequently, establishes a link 
to the closest neighbor in each quadrant of the plane. 
% With peer $J$ dividing the plane into four regions,
% the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
% establishes a link to the closest neighbor in each quadrant of the plane. 
%%
It does so, by starting from a known node in the neighborhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing are reduced and 
maintenance overhead is minimized.
A caching scheme is also used 
to further reduce routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node (i.e., number of links). 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round-trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4) with
each octet ranging from $1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

To optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia}~\cite{maymounkov_kademlia_2002} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by:
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with others, or 
  \item using a local database to look--up information.
\end{inparaenum}

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only $6\%$ 
to go through the backbone.
The behavior of \cite{KLKP2008} with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\emph{CHOP6} \cite{MT2007} is a Chord-variant DHT that exploits
{\sl IPv6} address format as well as available \emph{RTT} information to 
enable proximity estimation among peers during message routing.
%%
Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table with each entry now holding $k$$>$$1$ candidate
nodes. 
The next hop for a message is selected to be the one closest to the
destination among those $k$ candidate peers. 
This proximity is determined either
by exploiting RTT measurements or, if there is no such information yet 
(i.e., a new peer appears), by
estimating the distance in the overlay's ID space.

When joining the network, each node
receives a $64$-bit \emph{ID}. 
It comprises of a random part and the IPv6 prefix which 
is obtained by hashing the node's IP address and port
number; this combination is deployed in an effort  
to preserve the uniformity of node assignment. 
The prefix in question is based on IPv6's global routing prefix.
As IANA\footnote{\url{http://www.iana.org/}}  
assigns address blocks to regions (RIRs) which are further
distributed at national level (NIRs), the first $32$-bits of the address
can estimate the region or the country in which the node is connected. 
Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing. 
%%
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the three qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
Inter-\emph{AS} links are the costliest to ISPs and hence, 
minimizing topology mismatches greatly affects pertinent operational expenditure.
%%
To achieve this, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demonstrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portraying distance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
Administrators thus frequently
disable {\sl traceroute} support on their routers and this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbors into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{PChord}
\emph{PChord} \cite{HLYW2005} is based on the \emph{Chord DHT} and incorporates
proximity in its routing mechanism. 
To achieve this, the standard finger table
is augmented with a \emph{proximity list} that contains
nodes in the network found nearby in terms of RTT.
%in this way, the next hop can be decided based on both progress
%towards the key and the physical proximity of the candidate nodes.
%%AD
%% I am not sure about the "best progress" term - what does it really mean???
%% VM changed the above slightly to address the above comment. Generally
%% in DHTs when a node receives a search query for a key that it does not have
%% the data for, it routes the request to that node in its routing table that
%% is closest to the key. That is what I mean with best progress to the keys
%% In topology aware systems and topology aware routing we have the requirement
%% that the next hop should be the closest one which in many cases can be
%% a competing requirement with the best progress to the key requirement I
%% just described. 
In this respect, the next hop during routing can be decided based on both the
direction towards the search key and minimizing the cost of that hop.

When a peer joins the network, its proximity list is empty.
This list is maintained in a heuristic fashion during the node's lifetime.
When a node needs to route a message, it chooses as the next hop 
the node closest to the target key 
in \emph{both} its finger table and proximity list. 
An initial choice for the next hop made out of the finger list 
can be substituted by a shorter one from the proximity list if  
it is both closer to the key (ID-wise) and closer in physical distance.
This yields an equal or even more efficient routing than traditional Chord.
%% VM
%% Removed the text below that was a rephrasing of one of my own a little
%% bit more below. Hope it is way more clear now.
%%
% As there is always progress towards the target in the \emph{ID}-space,
% \emph{PChord} yields a reduced number of hopes that \emph{Chord}.
%%AD rephrased as above - the 2 last lines of the text below are 
%%		are difficult to decipher... 
% Due to the fact that, with each step, there is always 
% progress towards the target node in the ID space, 
% \emph{PChord} will result in a reduced hop number than
% Chord, since each hop in \emph{PChord} is larger or 
% at least equal in the key space.

@@

The \emph{ID} of an incoming node is computed based on 
both the identifier of the bootstrap node 
and the bootstrap's predecessor;
this is  done in a way that the \emph{ID} of the 
incoming peer is positioned \emph{between} the two identifiers mentioned above. 
After joining, a \emph{finger} table is created as in \emph{Chord}. 
Moreover, an \emph{adjacency table} maintains 
information about the $k$ closest--known peers. 
%%
The routing decision takes place in a way reminiscent to \emph{Chord}
and uses both adjacency and finger tables.
%%
\emph{AChord} behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% good routing efficiency but no adaptation to high churn environments.
medium &
% Relieves the system from joining overhead and topology aware ID construction
% but doubles the information needed to be stored and maintained by the
% introduction of adjacency table
medium &
% assumes the operation of ideal underlying any-cast mechanism (meaning that
% outside messages are always routed to the nearest node which in the current
% Internet, this is not always feasible. Moreover, is designed on the basis of
% IPv6 protocol which is not widely operational yet.
medium
\end{tabular}
}
\end{center}

@@

\emph{Chord6} reduces the average 
length of hops traversed
% system path length 
to be logarithmically proportional to the number 
of available domains instead of the number of participating peers. 
Due however to the large number of Internet
domains and the possibility of occasionally having only 
a small number of peers within each domain,
\cite{DK2006} challenges the approach's scalability and efficiency.
%%
Overall, the approach fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Can reduce inter-domain average path length but even though nodes in the same
% domain would have close identifiers, nodes in two close domains may have very
% different ones reducing the overall efficiency of the approach in general when
% considering inter-domain average path length. No active adaptation mechanism
% for high churn environments.
low &
% The construction of the identifier space is done at node join and in an
% independent fashion involving the application of two hash functions meaning
% resulting in low overhead stress to the network and its nodes.
low &
% Is designed on the basis of IPv6 protocol which is not widely operational yet.
low
\end{tabular}
}
\end{center}
